Procedural generation of levels for the Angry Birds videogame using evolutionary computation\\

### 2019-05-15 NOTarticle_english.tex

\title{Procedural generation of levels fot he angry birds videogame using
evolutionary computation\\
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Jaime Salinas-Hernández}
\IEEEauthorblockA{\textit{Department of Graduate Studies} \\
\textit{Tijuana Institute of Technology}\\
Tijuana, México \\
salinas.jaime1217@gmail.com}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Mario Garcia-Valdez}
\IEEEauthorblockA{\textit{Department of Graduate Studies} \\
\textit{Tijuana Institute of Technology}\\
Tijuana, México \\
mario@tectijuana.edu.mx}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
}

>>>>

\title{Procedural generation of levels for the Angry Birds videogame using
evolutionary computation\\
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Jaime Salinas-Hernández}
\IEEEauthorblockA{\textit{Department of Graduate Studies} \\
\textit{Tijuana Institute of Technology}\\
Tijuana, México \\
salinas.jaime1217@gmail.com}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Mario Garcia-Valdez}
\IEEEauthorblockA{\textit{Department of Graduate Studies} \\
\textit{Tijuana Institute of Technology}\\
Tijuana, México \\
mario@tectijuana.edu.mx}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Juan-J. Merelo-Guervós}
\IEEEauthorblockA{\textit{Dept. Computer Technology and Architecture} \\
\textit{University of Granada\\
Granada, Spain \\
jmerelo@ugr.es}
}
